### 2017-06-23 2017/NACO/paper.tex

The existence of several local optima essentially makes

@@

function \(\varphi(y(x))\), which satisfy the uniform H{\"o}lder condition i. e.

@@

\subsection{Core Multidimensional Algorithm of Global Search}
\label{subsec:corepar}
The information-statistical theory of global optimization formulated in \cite{strongin1978}, \cite{strSergGO} has
served as a basis for the development of a large number of efficient multiextremal optimization
methods \cite{barkalovGergel2014}, \cite{gergel1996}, \cite{gergel1997}, \cite{grishaginStrongin1984}, \cite{Pizzuti}, \cite{sergeyev1995}, \cite{sergeyev1999}, \cite{sergeyevGrishagin2001}, \cite{sergeyevStronginLera2013}, \cite{Famularo2001}.
\par
The optimization methods applied in Globalizer are based on the MAGS method, which can be presented as follows --- see \cite{strongin1978}, \cite{strSergGO}.
\par
Let us introduce a simpler notation for the optimization problem being solved
\begin{equation}
\label{eq:oneDimFunc}
f(x) = \varphi(y(x)):x\in [0,1].
\end{equation}
\par
The initial iteration of the algorithm is performed at an arbitrary point \mbox{\(x^1\in(0,1)\)}.
Then, let us suppose that \(k\), \(k\ge 1\), optimization iterations have been completed already.
The selection of the trial point \(x^{k+1}\) for the next iteration is performed according to the following rules.
\par
\textit{Rule 1}. Renumber the points of the preceding trials by the lower indices in order of increasing value of coordinates
\begin{equation}
  \label{step1}
0=x_0<x_1<...<x_{k+1}=1,
\end{equation}
the points \(x_0\), \(x_k\) were introduced additionally for the convenience of further
explanation, the values of the minimized function \(z_0\), \(z_k\) at these points are undefined.
\par
\textit{Rule 2}. Compute current estimate of the H{\"o}lder constant \(H\) from (\ref{eq:holder})
\begin{equation} \label{step2}
M=\max_{1\leq i\leq k}\frac{|z_i-z_{i-1}|}{\rho_i}, \;
m = \left\{
   \begin{array}{lr}
     rM, & M > 0,\\
     1, & M = 0,
   \end{array}
  \right.
\end{equation}
as the maximum of the relative differences of the minimized function values on the
set of previously executed trial points \(x_i,1\leq i\leq k\) from (\ref{step1}).
Hereafter, \(\rho_i=(x_i-x_{i-1})^\frac{1}{N},1\leq i\leq k+1\). The
constant \(r\), \(r>1\), is the reliability parameter of the algorithm.
\par
\textit{Rule 3}. Compute the characteristics \(R(i)\) for each interval \((x_{i-1},x_i),1\leq i\leq k+1\), where
\[
R(i)=2\rho_i-4\frac{z_i}{m},\quad i=1,
\]
\begin{equation} \label{step3}
R(i)=\rho_i+\frac{(z_i-z_{i-1})^2}{m^2\rho_i}-2\frac{z_i+z_{i-1}}{m},\quad 1<i<k+1, \\
\end{equation}
\[
R(i)=2\rho_{i}-4\frac{z_{i-1}}{m},\quad i=k+1.
\]

@@

\par
The stopping condition, which terminated the trials, is defined by the inequality
\begin{equation}
  \label{eq:stop_1}
\rho_t<\varepsilon
\end{equation}
for the interval with the maximum characteristic from (\ref{step4}) and \(\varepsilon >0\) is the predefined
accuracy of the optimization problem solution. If the stopping condition is not satisfied,
the index \(k\) is incremented by 1, and the new global optimization iteration is executed.
\par
In order to explain the algorithm presented above, let us note the following.
The characteristics \(R(i), 1\leq i\leq k+1\), calculated according to (\ref{step3}) could
be interpreted as some measures of importance of the intervals with respect to the
expected location of the global minimum point. Thus, the rules (\ref{step4}) and (\ref{step5}) for selecting
the interval for executing the next trial become more clear --- the point of every next
global optimization iteration is selected within the interval, where the global minimum
point can be found most likely.
\par
The convergence conditions of the described algorithm are given, for example, in \cite{strSergGO}.

@@

\begin{equation} \label{step5par}
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}-\mathrm{sign}(z_{t_j}-z_{t_j-1})\frac{1}{2r}\left[\frac{r|z_{t_j}-z_{t_j-1}|}{M}\right]^N,\; \textrm{ if } 1<t_j<k+1,
\end{equation}
\[
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2},\; \textrm{ if } t_j=1 \textrm{ or } t_j=k+1.
\]
\par
The stopping condition (\ref{eq:stop_1}) should be checked for all intervals from (\ref{step4par}),
where the scheduled trials are executed
\begin{equation}
  \label{eq:stop}
\rho_{t_j}<\varepsilon,1\leq j\leq p.
\end{equation}
If the stopping condition is satisfied at least for one interval \(t_j, 1\le j\le p\), the calculations
are terminated. Otherwise, the index \(k\) is incremented by \(p\), and new global optimization iteration is executed.
\par
The convergence conditions for the developed parallel algorithm are considered
in \cite{stronginGergelBarkalovParGO}, \cite{strSergGO}. Thus, in particular, when the convergence conditions are
satisfied, the parallel computations are non-redundant as compared to the serial method
when using up to \(2^N\) processors/cores (\(N\) is the dimensionality of the global optimization problem).

@@

    \item After completing any trial for any problem \(\varphi(y_l(x)),1\leq l\leq s\),

@@

    these should be included into the search information. The MAGS algorithm uses these
    accumulated data for the adaptive computing of the optimization iteration points (see Section \ref{subsec:corepar}).

@@

\section{Results of Numerical Experiments}
\label{sec:experiments}
The numerical experiments were carried out using the Lobachevsky supercomputer at
the State University of Nizhni Novgorod (the operation system – CentOS 6.4, the
supercomputer management system – SLURM). Each supercomputer node had 2 Intel Sandy Bridge
E5-2660 processors, 2.2 GHz, with 64 GB RAM. Each processor had 8 cores (i. e. total
16 CPU cores were available at each node). In order to generate the executable program code, the Intel C++ 14.0.2 compiler was used.
\par
A number of computational nodes had Intel Xeon Phi 5110P processors, each containing 60 cores
(total 240 threads). In addition, the supercomputer included the computational nodes equipped
with two NVIDIA Kepler K20X GPUs, each providing 14 stream multiprocessors (total 2688 CUDA-cores). In order to generate the executable code, the CUDA Toolkit 6.0 was used.
\par
In the performed experiments the optimization problems generated by the GKLS-generator
\cite{gavianoKvasovLeraSergeev2003} were used. This generator allows obtaining the multiextremal optimization
problems with \textit{a priori} known properties: the number of local minima, the sizes of the attractors of these ones, the global minimum point, the function value at this point, etc. In order to simulate the computational costs that are inherent in the applied optimization problems, in all experiments computing the objective function values was intentionally complicated by the auxiliary computations not altering the values of the function and the position of its minima.
\par
In all the executed experiments, 100 global optimization problems generated randomly by the GKLS-generator were solved. The results of experiments were averaged over the number of the solved optimization problems.

\subsection{Comparison with over methods}
The results of numerical comparison of three serial algorithms --- DIRECT
\cite{Jones}, DIRECT\textit{l} \cite{Gablonsky}, and MAGS from Section \ref{subsec:corepar} --- are presented below.

The numerical comparison was carried out by using the function classes Simple and Hard
of the dimensions 4 and 5. The results of numerical experiments for DIRECT and
DIRECT\textit{l} are taken from \cite{sergeyevKvasov2006}. According to \cite{sergeyevKvasov2006}, the global minimizer \(y^*\)
was considered to be found if the algorithm generated a trial point \(y^k\) inside
a hyperinterval with a vertex \(y^*\) and
\begin{displaymath}
    |y^k(i)-y^*(i)|\le \sqrt[N]{\Delta}(b(i)-a(i)), i\le i\le N,
\end{displaymath}
where \(N\) is the problem dimensionality, $a$ and $b$ are the borders of the search domain \(D\)
\footnote{In the case of MAGS, the stop condition was different slightly --- the
global minimizer \(y^*\) was considered to be found, if MAGS generates a trial
point \(y^k\)  in the \(\delta\)-vicinity of the global minimum, i. e. \(||y^k-y^*||\le\delta\).
The size of the vicinity was selected  as \(\delta=\left\|b-a\right\|\sqrt[N]{\Delta}\).}.

@@

In the second series of experiments, the parallel computations were executed using the CPUs.
The achieved relative speedup in iterations is shown in row II; the speedup of the
parallel computations is shown relative to the serial computations \((p=1)\).

The final series of experiments was executed using Xeon Phi processors. The results
of these experiments are shown in row III. In this case, the speedup is
calculated relative to the results of the PMAGS method executed on the CPU using eight cores \((p=8)\).

@@

\begin{table}
  \centering
  \caption{Speedup of parallel computations executed by GMAGS}
  \label{tab:5}
  \begin{tabular}{cccccccc}
    \cline{3-8}\noalign{\smallskip}
    \multicolumn{2}{c}{  } & \textit{p} & \multicolumn{2}{c}{$N=4$} & & \multicolumn{2}{c}{$N=5$}   \\
    \noalign{\smallskip} \cline{4-5} \cline{7-8}  \noalign{\smallskip}
    \multicolumn{2}{c}{  } & & \textit{Simple} & \textit{Hard} & & \textit{Simple} & \textit{Hard}  \\
    \noalign{\smallskip}\hline
    I &
    \parbox{0.25\textwidth}{
    \begin{center}
    \textbf{Serial trial computations.}\\ \textit{Average number} \\ \textit{of iterations}
    \end{center}		}
      & 1 & 11953 & 25263 & & 15920 & \(>\)148342 (4)  \\
    \hline \noalign{\smallskip}
II  & \textbf{Parallel computations}  %\multirow{3}{*}{}
  & 2 & 2.52 & 2.32 & & 1.21 & 1.41 \\
& of CPU. & 4 & 5.05 & 4.24 & & 3.13 & 2.92 \\
& \textit{Speedup} & 8 & 8.68 & 8.88 & & 4.24 & 6.66 \\
    \noalign{\smallskip}\hline	\noalign{\smallskip}
III & \textbf{Parallel computations} %\multirow{3}{*}{}
  & 60  & 8.18 & 7.37 & & 9.99 & 6.66  \\
&  of Xeon Phi. & 120 & 16.316 & 15.815 & & 15.215 & 17.317 \\
& \textit{Speedup} & 240 & 33.133 & 27.827 & & 38.838 & 59.359 \\

@@

\bibitem{barkalovGergel2014}
\newblock K. A. Barkalov and V. P. Gergel,
\newblock Multilevel scheme of dimensionality reduction for parallel global search algorithms,
\newblock in \emph{Proceedings of the 1st International Conference on
  Engineering and Applied Sciences Optimization}, (2014), 2111--2124.

@@

\bibitem{barkalovGergelLebedev2015}[10.1007/978-3-319-21909-7_31]
\newblock K. Barkalov, V. Gergel and I. Lebedev,
\newblock Use of XeonPhi coprocessor for solving global optimization problems,
\newblock \emph{LNCS}, \textbf{9251} (2015), 307--318.

@@

\bibitem{gergel1993}
\newblock V. P. Gergel,
\newblock A software system for multi-extremal optimization,
\newblock \emph{Eur. J. Oper. Res.}, \textbf{65(3)} (1993), 305--313.

\bibitem{gergel1996}
\newblock V. P. Gergel,
\newblock A method for using derivatives in the minimization of multiextremum functions,
\newblock \emph{Comput. Math. Math. Phys.}, \textbf{36(6)} (1996), 729--742.

\bibitem{gergel1997}[10.1023/A:1008290629896]
\newblock V. P. Gergel,
\newblock A global optimization algorithm for multivariate functions with Lipschitzian first derivatives,
\newblock \emph{J. Glob. Optim.}, \textbf{10(3)} (1997), 257--281.

\bibitem{gergel2013}[doi:10.1016/j.procs.2013.05.164]
\newblock V. P. Gergel, et al.,
\newblock High performance computing in biomedical applications,
\newblock \emph{Procedia Computer Science}, \textbf{18} (2013), 10--19.

\bibitem{gergel2015}[10.15866/ireaco.v8i1.4935]
\newblock V. P. Gergel, et al.,
\newblock Recognition of surface defects of cold-rolling sheets based on method of localities,
\newblock \emph{International Review of Automatic Control }, \textbf{8(1)} (2015), 51--55.

\bibitem{gergelSidorov2015}[10.1007/978-3-319-21909-7_49]
\newblock V. P. Gergel and S. V. Sidorov,
\newblock A two-level parallel global search algorithm for solving computationally intensive multi-extremal optimization problems,
\newblock \emph{LNCS}, \textbf{9251} (2015), 505--515.

@@

\bibitem{Pizzuti}[10.1007/s00211-002-0419-8]
\newblock D. E. Kvasov, C. Pizzuti and Y. D. Sergeyev,
\newblock Local tuning and partition strategies for diagonal go methods,
\newblock \emph{Numerische Mathematik}, \textbf{94(1)} (2003), 93--106.

@@

\bibitem{sergeyev1999}
\newblock Y. D. Sergeyev,
\newblock Multidimensional global optimization using the first derivatives,
\newblock \emph{Comput. Math. Math. Phys.}, \textbf{39(5)} (1999), 743--752,.

@@

\bibitem{strSergGO}[10.1007/978-1-4615-4677-1]
\newblock R.G. Strongin and Y.D. Sergeyev,
\newblock \emph{Global optimization with non-convex constraints. Sequential and parallel algorithms},
\newblock Kluwer Academic Publishers, Dordrecht (2000).

>>>>

The existence of several local optima makes

@@

function \(\varphi(y(x))\), which satisfy the uniform H{\"o}lder condition, i. e.

@@

\subsection{Core Multidimensional Algorithm of Global Search}
\label{subsec:corepar}
The information-statistical theory of global optimization formulated in \cite{strongin1978}, \cite{strSergGO} has
served as a basis for the development of a large number of efficient multiextremal optimization
methods \cite{barkalovGergel2014}, \cite{gergel1996}, \cite{gergel1997}, \cite{grishaginStrongin1984}, \cite{Pizzuti}, \cite{sergeyev1995}, \cite{sergeyev1999}, \cite{sergeyevGrishagin2001}, \cite{sergeyevStronginLera2013}, \cite{Famularo2001}.
\par
The optimization methods applied in Globalizer are based on the MAGS method, which can be presented as follows --- see \cite{strongin1978}, \cite{strSergGO}.
\par
Let us introduce a simpler notation for the optimization problem being solved
\begin{equation}
\label{eq:oneDimFunc}
f(x) = \varphi(y(x)):x\in [0,1].
\end{equation}
\par
The initial iteration of the algorithm is performed at an arbitrary point \mbox{\(x^1\in(0,1)\)}.
Then, let us suppose that \(k\), \(k\ge 1\), optimization iterations have been completed already.
The selection of the trial point \(x^{k+1}\) for the next iteration is performed according to the following rules.
\par
\textit{Rule 1}. Renumber the points of the preceding trials by the lower indices in order of increasing value of coordinates
\begin{equation}
  \label{step1}
0=x_0<x_1<...<x_{k+1}=1,
\end{equation}
the points \(x_0\), \(x_{k+1}\) were introduced additionally for the convenience of further
explanation, the values of the minimized function \(z_0\), \(z_{k+1}\) at these points are undefined.
\par
\textit{Rule 2}. Compute the current estimate of the H{\"o}lder constant \(H\) from (\ref{eq:holder})
\begin{equation} \label{step2}
M=\max_{1 < i\leq k}\frac{|z_i-z_{i-1}|}{\rho_i}, \;
m = \left\{
   \begin{array}{lr}
     rM, & M > 0,\\
     1, & M = 0,
   \end{array}
  \right.
\end{equation}
as the maximum of the relative differences of the minimized function values on the
set of previously executed trial points \(x_i,1\leq i\leq k\) from (\ref{step1}).
Hereafter, \(\rho_i=(x_i-x_{i-1})^\frac{1}{N},1\leq i\leq k+1\). The
constant \(r\), \(r>1\), is the reliability parameter of the algorithm.
\par
\textit{Rule 3}. Compute the characteristics \(R(i)\) for each interval \((x_{i-1},x_i),1\leq i\leq k+1\), where
\[
R(i)=2\rho_i-4\frac{z_i}{m},\quad i=1,
\]
\begin{equation} \label{step3}
R(i)=\rho_i+\frac{(z_i-z_{i-1})^2}{m^2\rho_i}-2\frac{z_i+z_{i-1}}{m},\quad 1<i<k+1, \\
\end{equation}
\[
R(i)=2\rho_{i}-4\frac{z_{i-1}}{m},\quad i=k+1.
\]

@@

\par
The stopping condition, which terminated the trials, is defined by the inequality
\begin{equation}
  \label{eq:stop_1}
\rho_t<\varepsilon
\end{equation}
for the interval with the maximum characteristic from (\ref{step4}) and \(\varepsilon >0\) is the predefined
accuracy of the optimization problem solution. If the stopping condition is not satisfied,
the index \(k\) is incremented by 1, and the new global optimization iteration is executed.
\par
In order to explain the algorithm presented above, let us note the following.
The characteristics \(R(i), 1\leq i\leq k+1\), calculated according to (\ref{step3}) could
be interpreted as some measures of importance of the intervals with respect to the
expected location of the global minimum point. Thus, the rules (\ref{step4}) and (\ref{step5}) for selecting
the interval of the next trial become more clear --- the point of every next
global optimization iteration is selected within the interval, where the global minimum
point can be found most likely.
\par
The convergence conditions of the described algorithm are given, for example, in \cite{strSergGO}.

@@

\begin{equation} \label{step5par}
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}-\mathrm{sign}(z_{t_j}-z_{t_j-1})\frac{1}{2r}\left[\frac{r|z_{t_j}-z_{t_j-1}|}{m}\right]^N,\; \textrm{ if } 1<t_j<k+1,
\end{equation}
\[
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2},\; \textrm{ if } t_j=1 \textrm{ or } t_j=k+1.
\]
\par
The stopping condition (\ref{eq:stop_1}) should be checked for all intervals from (\ref{step4par}),
where the scheduled trials are executed
\begin{equation}
  \label{eq:stop}
\rho_{t_j}<\varepsilon,1\leq j\leq p.
\end{equation}
If the stopping condition is satisfied at least for one interval \(t_j, 1\le j\le p\), the calculations
are terminated. Otherwise, the index \(k\) is incremented by \(p\), and new global optimization iteration is executed.
\par
The convergence conditions for the developed parallel algorithm are considered
in \cite{stronginGergelBarkalovParGO}, \cite{strSergGO}. Thus, in particular, when the convergence conditions are
satisfied, the parallel computations are non-redundant as compared to the serial method
when using up to \(2^N\) processors/cores (\(N\) is the dimensionality of the global optimization problem).

@@

    \item After completing any trial for any problem \(\varphi(y^l(x)),1\leq l\leq s\),

@@

    these should be included into the search information. The PMAGS algorithm uses these
    accumulated data for the adaptive computing of the optimization iteration points (see Section \ref{subsec:sharedpar}).

@@

\section{Results of Numerical Experiments}
\label{sec:experiments}
The numerical experiments were carried out using the Lobachevsky supercomputer at
the State University of Nizhni Novgorod (the operation system – CentOS 6.4, the
supercomputer management system – SLURM). Each supercomputer node had 2 Intel Sandy Bridge
E5-2660 2.2 GHz processors with 64 GB RAM. Each processor had 8 cores (i. e. total
16 CPU cores were available at each node). In order to generate the executable program code, the Intel C++ 14.0.2 compiler was used.
\par
A number of computational nodes had Intel Xeon Phi 5110P processors, each containing 60 cores
(total 240 threads). In addition, the supercomputer included the computational nodes equipped
with two NVIDIA Kepler K20X GPUs, each providing 14 stream multiprocessors (total 2688 CUDA-cores). In order to generate the executable code, the CUDA Toolkit 6.0 was used.
\par
In the performed experiments the optimization problems generated by the GKLS-generator
\cite{gavianoKvasovLeraSergeev2003} were used. This generator allows obtaining the multiextremal optimization
problems with \textit{a priori} known properties: the number of local minima, the sizes of the attractors of these ones, the global minimum point, the function value at this point, etc. In order to simulate the computational costs that are inherent in the applied optimization problems, in all experiments computing the objective function values was intentionally complicated by the auxiliary computations not altering the values of the function and the position of its minima.
\par
In all the executed experiments, 100 global optimization problems generated randomly by the GKLS-generator were solved. The results of experiments were averaged over the number of the solved optimization problems.

\subsection{Comparison with other methods}
The results of numerical comparison of three serial algorithms --- DIRECT
\cite{Jones}, DIRECT\textit{l} \cite{Gablonsky}, and MAGS from Section \ref{subsec:corepar} --- are presented below.

The numerical comparison was carried out by using the function classes Simple and Hard
of the dimensions 4 and 5. The results of numerical experiments for DIRECT and
DIRECT\textit{l} are taken from \cite{sergeyevKvasov2006}. According to \cite{sergeyevKvasov2006}, the global minimizer \(y^*\)
was considered to be found if the algorithm generated a trial point \(y^k\) inside
a hyperinterval with a vertex \(y^*\) and
\begin{displaymath}
    |y^k(i)-y^*(i)|\le \sqrt[N]{\Delta}(b(i)-a(i)), 1 \le i\le N,
\end{displaymath}
where \(N\) is the problem dimensionality, $a$ and $b$ are the borders of the search domain \(D\)
\footnote{In the case of MAGS, the stop condition was different slightly --- the
global minimizer \(y^*\) was considered to be found, if MAGS generates a trial
point \(y^k\)  in the \(\delta\)-vicinity of the global minimum, i. e. \(||y^k-y^*||\le\delta\).
The size of the vicinity was selected  as \(\delta=\left\|b-a\right\|\sqrt[N]{\Delta}\).}.

@@

In the second series of experiments, the parallel computations were executed using PMAGS on CPUs.
The achieved relative speedup in iterations is shown in row II; the speedup of the
parallel computations is shown relatively to the serial computations \((p=1)\).

The final series of experiments was executed using Xeon Phi processors. The results
of these experiments are shown in row III. In this case, the speedup is
calculated relatively to the results of the PMAGS method executed on the CPU using eight cores \((p=8)\).

@@

\begin{table}
  \centering
  \caption{Speedup of parallel computations executed by GPMAGS}
  \label{tab:5}
  \begin{tabular}{cccccccc}
    \cline{3-8}\noalign{\smallskip}
    \multicolumn{2}{c}{  } & \textit{p} & \multicolumn{2}{c}{$N=4$} & & \multicolumn{2}{c}{$N=5$}   \\
    \noalign{\smallskip} \cline{4-5} \cline{7-8}  \noalign{\smallskip}
    \multicolumn{2}{c}{  } & & \textit{Simple} & \textit{Hard} & & \textit{Simple} & \textit{Hard}  \\
    \noalign{\smallskip}\hline
    I &
    \parbox{0.25\textwidth}{
    \begin{center}
    \textbf{Serial trial computations.}\\ \textit{Average number} \\ \textit{of iterations}
    \end{center}		}
      & 1 & 11953 & 25263 & & 15920 & \(>\)148342 (4)  \\
    \hline \noalign{\smallskip}
II  & \textbf{Parallel computations}  %\multirow{3}{*}{}
  & 2 & 2.52 & 2.32 & & 1.21 & 1.41 \\
& of CPU. & 4 & 5.05 & 4.24 & & 3.13 & 2.92 \\
& \textit{Speedup} & 8 & 8.68 & 8.88 & & 4.24 & 6.66 \\
    \noalign{\smallskip}\hline	\noalign{\smallskip}
III & \textbf{Parallel computations} %\multirow{3}{*}{}
  & 60  & 8.18 & 7.37 & & 9.99 & 6.66  \\
&  of Xeon Phi. & 120 & 16.316 & 15.815 & & 15.215 & 17.317 \\
& \textit{Speedup} & 240 & 33.133 & 27.827 & & 38.838 & 59.359 \\

@@

\bibitem{barkalovGergel2014}
\newblock K. Barkalov and V. Gergel,
\newblock Multilevel scheme of dimensionality reduction for parallel global search algorithms,
\newblock in \emph{Proceedings of the 1st International Conference on
  Engineering and Applied Sciences Optimization}, (2014), 2111--2124.

@@

\bibitem{barkalovGergelLebedev2015}[10.1007/978-3-319-21909-7_31]
\newblock K. Barkalov, V. Gergel and I. Lebedev,
\newblock Use of Xeon Phi coprocessor for solving global optimization problems,
\newblock \emph{LNCS}, \textbf{9251} (2015), 307--318.

@@

\bibitem{gergel1993}
\newblock V. Gergel,
\newblock A software system for multi-extremal optimization,
\newblock \emph{Eur. J. Oper. Res.}, \textbf{65(3)} (1993), 305--313.

\bibitem{gergel1996}
\newblock V. Gergel,
\newblock A method for using derivatives in the minimization of multiextremum functions,
\newblock \emph{Comput. Math. Math. Phys.}, \textbf{36(6)} (1996), 729--742.

\bibitem{gergel1997}[10.1023/A:1008290629896]
\newblock V. Gergel,
\newblock A global optimization algorithm for multivariate functions with Lipschitzian first derivatives,
\newblock \emph{J. Glob. Optim.}, \textbf{10(3)} (1997), 257--281.

\bibitem{gergel2013}[doi:10.1016/j.procs.2013.05.164]
\newblock V. Gergel, et al.,
\newblock High performance computing in biomedical applications,
\newblock \emph{Procedia Computer Science}, \textbf{18} (2013), 10--19.

\bibitem{gergel2015}[10.15866/ireaco.v8i1.4935]
\newblock V. Gergel, et al.,
\newblock Recognition of surface defects of cold-rolling sheets based on method of localities,
\newblock \emph{International Review of Automatic Control }, \textbf{8(1)} (2015), 51--55.

\bibitem{gergelSidorov2015}[10.1007/978-3-319-21909-7_49]
\newblock V. Gergel and S. Sidorov,
\newblock A two-level parallel global search algorithm for solving computationally intensive multi-extremal optimization problems,
\newblock \emph{LNCS}, \textbf{9251} (2015), 505--515.

@@

\bibitem{Pizzuti}[10.1007/s00211-002-0419-8]
\newblock D. E. Kvasov, C. Pizzuti and Y. D. Sergeyev,
\newblock Local tuning and partition strategies for diagonal GO methods,
\newblock \emph{Numerische Mathematik}, \textbf{94(1)} (2003), 93--106.

@@

\bibitem{sergeyev1999}
\newblock Y. D. Sergeyev,
\newblock Multidimensional global optimization using the first derivatives,
\newblock \emph{Comput. Math. Math. Phys.}, \textbf{39(5)} (1999), 743--752.

@@

\bibitem{strSergGO}[10.1007/978-1-4615-4677-1]
\newblock R. G. Strongin and Y. D. Sergeyev,
\newblock \emph{Global optimization with non-convex constraints. Sequential and parallel algorithms},
\newblock Kluwer Academic Publishers, Dordrecht (2000, 2nd ed. 2013, 3rd ed. 2014).
